\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-11 poster/main.tex
update posters

\begin{block}{Bayesian inference ($\bysinfer$): Example: Beta-Binomial model}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
%The prior $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$ is conjugate to the likelihood function.
\begin{itemize}
  \item[-] Prior on $\theta: \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data set $\dataobs= (x_1,\dots x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.

@@

We define the mechanism $\hexpmech$ which produces an element $r$ in $\betaset$ with probaiblity:
\[
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
\frac 
{\exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
{\sum_{r\in\betaset} \exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
\]

@@

\begin{block}{Preliminary Experimental Results}
% Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
Experiments are on three mechanisms and plotted as follows:
\begin{itemize}
  \item[-] Green: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
  \item[-] Red: LapMech with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
  (posteriors of adjacent data sets differ only in two dimensions).
  \item[-] Blue: $\hexpmech$.
\end{itemize}
  Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size or prior configuration.

@@

Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} give us the discrete probabilities. On the x-axis: the distance of a potential output r from the true answer and on y-axis the probability of r being output by the mechanisms.
\begin{figure}[H]
\begin{center}
\centering
   \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.31\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.311\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.311\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\caption{4-quantile and discrete probability plots}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}

>>>>

\begin{block}{Bayesian inference ($\bysinfer$) (A Beta-Binomial model example):}
% The first subdivided column within the first main column
% \begin{columns} % Subdivide the first main column
% \begin{column}{.54\textwidth} % The first subdivided column within the first main column
%The prior $\betad(\alpha, \beta)$, with hyperparameters $\alpha,\beta\in\mathbb{R}^{+}$ is conjugate to the likelihood function.
\begin{itemize}
  \item[-] Prior on $\theta: \betad(\alpha, \beta), \alpha,\beta\in\mathbb{R}^{+}$, observed data set $\dataobs= (x_1,\dots x_n)\in\{0,1\}^{n}, n\in\mathbb{N}$.

@@

We define the mechanism $\hexpmech$ which produces an element $r$ in $\betaset$ with probaiblity:
\[
% \underset{z \thicksim \hexpmech}{\Pr}[z=r] = 
\mathbb{P}_{r \thicksim \hexpmech} =
\frac 
{\exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
{\sum_{r\in\betaset} \exp \Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\Big)}
\]

@@

\begin{block}{Preliminary Experimental Results}
% Two groups of experimental results both with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$.
Experiments are on three mechanisms and plotted as follows:
\begin{itemize}
  \item[-] \textbf{Green}: Baseline approach. (noises being postprocessed to floor value) %adds noise scaled to sensitivity proportional to dimensionality,
  \item[-] \textbf{Red}: LapMech with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
  (posteriors of adjacent data sets differ only in two dimensions).
  \item[-] \textbf{Blue}: $\hexpmech$.
\end{itemize}
  Fig. \ref{fig_sampling} and Fig. \ref{subfig_prior} give us the average and 4-quantile of Hellinger distance between the sampled results and true posterior, by sampling for $10k$ times under each data size or prior configuration.

@@

Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} give us the discrete probabilities. On the x-axis: the distance of a potential output r from the true answer and on y-axis the probability of r being output by the mechanisms.
\begin{figure}[H]
\begin{center}
\centering
   \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.313\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\caption{4-quantile and discrete probability plots}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}
